---
title: "Web scraping - Project 1"
author: "David Utassy"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(moments)
library(data.table)
```

## Overview

This is the output document of [**Project 1**](https://ceuedu-my.sharepoint.com/:x:/g/personal/orsosm_ceu_edu/ETc-Mf_JpbRPjSdH2t3d6ScB_z0xBrn8RmR4HtLx37_-xg?e=lDFYFj) for Web Srcaping in R. This project is created by David Utassy and its main purpose is to practice the basics of Web Scraping. The code scrapes [**www.jofogas.hu**](https://www.jofogas.hu/) with a given search term and the number of pages to scrape. 

## Function to scrape one page

```{r}
get_one_page_from_jofogas  <- function(my_url) {
  print(my_url)
  t <- read_html(my_url)
  boxes <- t %>% 
    html_nodes('.contentArea')
  x <- boxes[[1]]
  
  boxes_df <- lapply(boxes, function(x){
    t_list <- list()
    t_list[['title']] <- x %>% html_nodes('.subject') %>% html_text()
    t_list[['link']] <- x %>% html_nodes('.subject') %>% html_attr('href')
    t_list[['price']]  <- x %>% html_nodes('.price-value') %>% html_text()
    t_list[['category']]  <- x %>% html_nodes('.category') %>% html_text()
    t_list[['location']]  <- x %>% html_nodes('.cityname') %>% html_text()
    t_list[['upload_time']]  <- x %>% html_nodes('.time') %>% html_text()
    return(data.frame(t_list))  
  })
  
  df <- rbindlist(boxes_df)
  return(df)
}
```

## A definable funtion to srape according to given searchterm and given number of pages 

```{r}
get_jofogas <- function(searchterm, page_to_download) {
  # create links
 links_to_get <- 
  paste0('https://www.jofogas.hu/magyarorszag?q=',searchterm, '&o=', seq(1, page_to_download))
 ret_df <- rbindlist(lapply(links_to_get, get_one_page_from_jofogas))
  return(ret_df)
}
```

``` {r, message=FALSE}
df <- get_jofogas(searchterm = 'asztal', 3)
knitr::kable(df)
```